---
title: "MATH 656 Final Project"
date: "2022-12-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn=-1)
```


```{r}
MyPersonality<- read.csv("Mypersonality.csv", header=TRUE)
```

## Prepare the Data
```{r}
Personality<- MyPersonality[,-3:-8]
#Personality
```

# Dealing with missing values
```{r}
P_na<-Personality[6400,]
Personality[6400,][2]<-'To those with interest in international politics and policy I recommend : "THE POST-AMERICAN WORLD" By *PROPNAME*'
Personality[6400,][3]<- 254.0
Personality[6400,][4]<- 29724.90
Personality[6400,][5]<- 93.25	
Personality[6400,][6]<- 0.04	
Personality[6400,][7]<-30978.00
Personality[6400,][8]<-0.49
Personality[6400,][9]<-0.18
which(is.na(Personality))
```

```{r,warning=FALSE}
library(tidyverse)
library(stringr)
library(NLP)
library(tm)
library(SnowballC)
library(factoextra)
library(dplyr)
library(tidytext)
library(textdata)
```


#Count the number of the posts by each user
```{r}
Personality1<-Personality %>%
     group_by(X.AUTHID) %>% arrange(STATUS) %>%
     summarise(STATUS1=paste(STATUS,collapse=","),num_of_post=length(STATUS),NETWORKSIZE=NETWORKSIZE,BETWEENNESS=BETWEENNESS,NBETWEENNESS=NBETWEENNESS,DENSITY=DENSITY,BROKERAGE=BROKERAGE,NBROKERAGE=NBROKERAGE,TRANSITIVITY=TRANSITIVITY,cEXT=cEXT,cNEU=cNEU,cAGR=cAGR,cCON=cCON,cOPN=cOPN)%>%
     arrange(desc(num_of_post), STATUS1)
Personality1<-Personality1 %>% distinct(X.AUTHID, .keep_all = T)
Personality1$index <- 1:nrow(Personality1)
#Personality1
```

```{r}
n=250
Per_feature<-Personality1[1:n,c(3,4,6,7,9,10,16)]
Big5<-Personality1[1:n,c(11:16)]
```


```{r}
colnames(Personality1)[16] <- "doc_id"
colnames(Personality1)[2] <- "text"
Per<-Personality1[1:n,c(2,16)]
```

# keep the emojis and acronyms
```{r}
smiles <- data.frame(s=c(":)",":(",";)",":D","<3","lol"),
                     r=c("happyParen","unhappyParen","winkSmilen","DSmilen","heartParen","hhhParen"))

library(stringi)
## replace smiley with text
Per$text <- stri_replace_all_fixed(Per$text,pattern = smiles$s,replacement = smiles$r,vectorize_all = FALSE)
## remove punctuation
Per$text <- gsub("[^a-z]", " ", Per$text, ignore.case = TRUE)
#Per
```


```{r}
nrc<-get_sentiments(lexicon = "nrc")
```

```{r,warning=FALSE}
clean.corpus<-function(corpus){
  #corpus<-tm_map(corpus,PlainTextDocument)
  corpus<-tm_map(corpus,removePunctuation) #Remove Punctuations
  corpus<- tm_map(corpus,content_transformer(tolower)) #Makes all text lowercase
  corpus<-tm_map(corpus,removeNumbers)#Remove numbers
  corpus<-tm_map(corpus,stripWhitespace) #Removes tabs and extra spaces
  #corpus<-tm_map(corpus, stemDocument)# Perform word stemming

  corpus<-tm_map(corpus, removeWords, stopwords("english")) #Remove common stopwords

  # corpus<-tm_map(corpus,content_transformer(tryTolower))
  # corpus<-tm_map(corpus,removeWords,custom.stopwords)
  # corpus<-tm_map(corpus,removePunctuation)
  # corpus<-tm_map(corpus,stripWhitespace)
  # corpus<-tm_map(corpus,removeNumbers)
  return(corpus)
}
```



```{r}
st.corp<-VCorpus(VectorSource(Per$text[1]))
st.corp<-clean.corpus(st.corp)
st.dtm<-DocumentTermMatrix(st.corp)
st.tidy<-tidy(st.dtm)
colnames(st.tidy)<-c("index","word","count")

sentiment_t<-inner_join(st.tidy,nrc)

sentiment_t<-count(sentiment_t,sentiment)
colnames(sentiment_t)<-c("sentiment",1)
```




```{r}
for (j in 2:250){
  st.corp<-VCorpus(VectorSource(Per$text[j]))
  st.corp<-clean.corpus(st.corp)
  st.dtm<-DocumentTermMatrix(st.corp)
  st.tidy<-tidy(st.dtm)
  colnames(st.tidy)<-c("index","word","count")

  st.sentiment<-inner_join(st.tidy,nrc)
  st.sentiment<-count(st.sentiment,sentiment)
  colnames(st.sentiment)<-c("sentiment",j)
  #st.sentiment<-spread(st.sentiment,sentiment,n,fill=0)
  sentiment_t<-merge(sentiment_t,st.sentiment,by="sentiment", all.x = TRUE)
}
```

```{r}
sentiment<-t(sentiment_t)
sentiment<-as.data.frame(sentiment)
colnames(sentiment) <- sentiment[1,]
sentiment <- sentiment[-1,]
sentiment[is.na(sentiment)]<-0
sentiment=as.data.frame(lapply(sentiment,as.numeric))
```


```{r}
senti_feature<-cbind(Per_feature,sentiment)
```

```{r}
Pers_corpus <- VCorpus(DataframeSource(Per))
#Pers_corpus[[4]]
```


```{r}
# text mining
Pers_corpus<-tm_map(Pers_corpus,PlainTextDocument)
Pers_corpus<-tm_map(Pers_corpus,removePunctuation) #Remove Punctuations
Pers_corpus <- tm_map(Pers_corpus,content_transformer(tolower)) #Makes all text lowercase
Pers_corpus<-tm_map(Pers_corpus,removeNumbers)#Remove numbers
Pers_corpus<-tm_map(Pers_corpus,stripWhitespace) #Removes tabs and extra spaces
Pers_corpus<-tm_map(Pers_corpus, stemDocument)# Perform word stemming
 
Pers_corpus<-tm_map(Pers_corpus, removeWords, stopwords("english")) #Remove common stopwords

```

```{r}
# form a particular stop word list
myStopwords <- c("can", "say","one","way","use",
                                   "also","howev","tell","will",
                                   "much","need","take","tend","even",
                                   "particular","rather","said",
                                   "get","well","make","ask","come","end",
                                   "first","two","help","often","may",
                                   "might","see","someth","thing","point",
                                   "post","look","right","now","think","’ve ",
                                   "’re ","propname","propnam","just","tri")
Pers_corpus <- tm_map(Pers_corpus, removeWords, myStopwords)
```


#Making a document-term matrix
```{r}
# Create the dtm from the corpus: 
Pers_dtm <- DocumentTermMatrix(Pers_corpus)
```

```{r}
# Convert Pers_dtm to a matrix
Pers_m <- as.matrix(Pers_dtm)
# Print the dimensions of Pers_dtm
dim(Pers_m)
```


```{r}
d<-c("happyparen","unhappyparen","winksmilen","dsmilen","heartparen","hhhparen")
Pers_smile<-Pers_m[1:n,d]
Pers_smile<-as.data.frame(Pers_smile)
Pers_smile$index <- 1:nrow(Pers_smile)
```


```{r}
# Since the sparsity is so high, we remove some of these low frequency terms
Pers_dtm_rm_sparse <- removeSparseTerms(Pers_dtm, 0.8) 
Pers_m <- as.matrix(Pers_dtm_rm_sparse)
dim(Pers_m)
```


```{r}
Pers_word<-as.data.frame(Pers_m)

Pers_word$index <- 1:nrow(Pers_word)
```


```{r}
# obtain the data prepared for clustering
total <- merge(senti_feature,Pers_smile,by="index")
total_Per <- merge(total,Pers_word,by="index")
total_Per<-select(total_Per,-matches("en.y"))
total_Per1<-select(total_Per,-matches("index"))
#total_Per1
```

## K-means clustering
```{r,warning=FALSE}
library(magrittr) # needs to be run every time you start R and want to use %>%
# scale_numeric <- function(x) x %>% mutate_if(is.numeric, function(y) as.vector(scale(y))) 
# Per_scaled <- total_Per1 %>% scale_numeric() 
```



```{r}
# Determine number of clusters (K-means)
n = 10
clust = numeric(n)
for (i in 1:n){
  clust[i] = kmeans(total_Per1, i, nstart = 20)$tot.withinss
}
plot(1:10, clust, col = "darkred", lwd = 3, xlab = "Number of Clusters", type = "b",
     ylab = "Total Within Cluster SS", col.axis = "navyblue")
abline(v=4, lty=2)
```

```{r}
ks <- 2:10
d <- dist(total_Per1)
str(d)
ASW <- sapply(ks, FUN=function(k) {
  fpc::cluster.stats(d, kmeans(total_Per1, centers=k, nstart = 5)$cluster)$avg.silwidth
  })

best_k <- ks[which.max(ASW)]
best_k
ggplot(as_tibble(ks, ASW), aes(ks, ASW)) + geom_line() +
  geom_vline(xintercept = best_k, color = "red", linetype = 2)
```


```{r}
set.seed(656)
clu=4
km <- kmeans(total_Per1, centers = clu, nstart = 10) 
km
```

```{r}
fviz_cluster(km, data = total_Per1, ellipse.type = "convex", palette = "jco", repel = TRUE, ggtheme = theme_minimal())
```


```{r}
total_Per_clustered <- total_Per1 %>% add_column(cluster = factor(km$cluster)) 
```

```{r}
ggplot(total_Per_clustered, aes(x = num_of_post, y = NETWORKSIZE,color=cluster)) + geom_point()
```

```{r}
centroids <- as_tibble(km$centers, rownames = "cluster")
centroids
```

```{r}
total_Per.pca1<-prcomp(total_Per1,center=TRUE, scale = TRUE)
#summary(total_Per.pca1)
#fviz_eig(total_Per.pca1)
```

```{r}
total_Per_transform = as.data.frame(-total_Per.pca1$x[,1:2])
set.seed(656)
km1 <- kmeans(total_Per_transform, centers = clu)
fviz_cluster(km1, data = total_Per_transform,centroids = TRUE, repel = TRUE, ellipse.type = "convex")
```


```{r}
# check outliers
total_Per[c(4,10,16),]
```

```{r}
total_Per_clustered1<-total_Per_clustered[total_Per_clustered$cluster==1,]
#total_Per_clustered1
total_Per_clustered2<-total_Per_clustered[total_Per_clustered$cluster==2,]
#total_Per_clustered2
```


```{r}
Big5_1 <- Big5 %>% add_column(cluster = factor(km$cluster)) 
Big5_1<-select(Big5_1,-matches("index"))
```

```{r}
Big5_2<-Big5_1
Big5_2[,c(1:5)][Big5_2[,c(1:5)]=="y"]="1"
Big5_2[,c(1:5)][Big5_2[,c(1:5)]=="n"]="0"
```

#Conduct one-way analysis of variance regarding personality class
```{r}
#conduct ANOVA for cEXT
aov1 <- aov(cEXT~cluster, Big5_2)
aov1
summary(aov1)
```

```{r}
#conduct ANOVA for cNEU
aov2 <- aov(cNEU~cluster, Big5_2)
aov2
summary(aov2)
```

```{r}
#conduct ANOVA for cAGR
aov3 <- aov(cAGR~cluster, Big5_2)
aov3
summary(aov3)
```

```{r}
#conduct ANOVA for cCON
aov4 <- aov(cCON~cluster, Big5_2)
aov4
summary(aov4)
```

```{r}
#conduct ANOVA for cOPN
aov5 <- aov(cOPN~cluster, Big5_2)
aov5
summary(aov5)
```

```{r,warning=FALSE}
library(ggplot2)
library(reshape2)
```

#Bar chart for the distribution of each personality trait
```{r}
#cEXT
Y<-c(0,0,0,0)
N<-c(0,0,0,0)
a<-data.frame(N,Y)
Cluster_k<-c(1:4)
cEXT_k<-cbind(Cluster_k,a)
cEXT_k_p<-cEXT_k
for(l in 1:clu){
  Big5_clus=Big5_1[Big5_1$cluster == as.character(l),]
  for(p in 1:2){
  cEXT_k[l,(p+1)]<-as.numeric(table(Big5_clus[,1]))[p]
  cEXT_k_p[l,(p+1)]<-as.numeric(table(Big5_clus[,1]))[p]/km$size[l]
  }
}
cEXT_k
cEXT_k_p

cEXT_k_p <- melt(cEXT_k_p, id.vars = 1)
ggplot(cEXT_k_p, aes(Cluster_k, value, fill = variable)) + 
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Sociable vs Shy") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  ) 
```


```{r}
#cNEU
cNEU_k<-cbind(Cluster_k,a)
cNEU_k_p<-cNEU_k
for(l in 1:clu){
  Big5_clus=Big5_1[Big5_1$cluster == as.character(l),]
  for(p in 1:2){
  cNEU_k[l,(p+1)]<-as.numeric(table(Big5_clus[,2]))[p]
  cNEU_k_p[l,(p+1)]<-as.numeric(table(Big5_clus[,2]))[p]/km$size[l]
  }
}
cNEU_k
cNEU_k_p

cNEU_k_p <- melt(cNEU_k_p, id.vars = 1)
ggplot(cNEU_k_p, aes(Cluster_k, value, fill = variable)) + 
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Neurotic vs Calm") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  ) 
```

```{r}
#cAGR
cAGR_k<-cbind(Cluster_k,a)
cAGR_k_p<-cAGR_k
for(l in 1:clu){
  Big5_clus=Big5_1[Big5_1$cluster == as.character(l),]
  for(p in 1:2){
  cAGR_k[l,(p+1)]<-as.numeric(table(Big5_clus[,3]))[p]
  cAGR_k_p[l,(p+1)]<-as.numeric(table(Big5_clus[,3]))[p]/km$size[l]
  }
}
cAGR_k
cAGR_k_p

cAGR_k_p <- melt(cAGR_k_p, id.vars = 1)
ggplot(cAGR_k_p, aes(Cluster_k, value, fill = variable)) + 
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Friendly vs Uncooperative") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  ) 
```

```{r}
#cCON
cCON_k<-cbind(Cluster_k,a)
cCON_k_p<-cCON_k
for(l in 1:clu){
  Big5_clus=Big5_1[Big5_1$cluster == as.character(l),]
  for(p in 1:2){
  cCON_k[l,(p+1)]<-as.numeric(table(Big5_clus[,4]))[p]
  cCON_k_p[l,(p+1)]<-as.numeric(table(Big5_clus[,4]))[p]/km$size[l]
  }
}
cCON_k
cCON_k_p

cCON_k_p <- melt(cCON_k_p, id.vars = 1)
ggplot(cCON_k_p, aes(Cluster_k, value, fill = variable)) + 
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Organized vs Careless") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  ) 
```

```{r}
#cOPN
cOPN_k<-cbind(Cluster_k,a)
cOPN_k_p<-cOPN_k
for(l in 1:clu){
  Big5_clus=Big5_1[Big5_1$cluster == as.character(l),]
  for(p in 1:2){
  cOPN_k[l,(p+1)]<-as.numeric(table(Big5_clus[,5]))[p]
  cOPN_k_p[l,(p+1)]<-as.numeric(table(Big5_clus[,5]))[p]/km$size[l]
  }
}
cOPN_k
cOPN_k_p

cOPN_k_p <- melt(cOPN_k_p, id.vars = 1)
ggplot(cOPN_k_p, aes(Cluster_k, value, fill = variable)) + 
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Insightful vs Unimaginative") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  ) 
```

#Distribution of personality traits for each cluster formed by K-means
```{r}
#Cluster 1
Y<-c(0,0,0,0,0)
N<-c(0,0,0,0,0)
b<-data.frame(N,Y)
Type_k<-c("x-typed","n-typed","a-typed","c-typed","o-typed")
c1_k<-cbind(Type_k,b)
c1_k_p<-c1_k
Big5_clus=Big5_1[Big5_1$cluster == as.character(1),]
for(r in 1:5){
  for(s in 1:2){
    #c1_k[r,(s+1)]<-as.numeric(table(Big5_clus[,1]))[s]
    c1_k_p[r,(s+1)]<-as.numeric(table(Big5_clus[,r]))[s]/km$size[1]
  }
}
c1_k_p

c1_k_p <- melt(c1_k_p, id.vars = 1)
ggplot(c1_k_p, aes(Type_k, value, fill = variable)) +
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Cluster 1") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  )
```

```{r}
#Cluster 2
c2_k<-cbind(Type_k,b)
c2_k_p<-c2_k
Big5_clus=Big5_1[Big5_1$cluster == as.character(2),]
for(r in 1:5){
  for(s in 1:2){
    c2_k_p[r,(s+1)]<-as.numeric(table(Big5_clus[,r]))[s]/km$size[2]
  }
}
c2_k_p

c2_k_p <- melt(c2_k_p, id.vars = 1)
ggplot(c2_k_p, aes(Type_k, value, fill = variable)) +
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Cluster 2") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  )
```

```{r}
#Cluster 3
c3_k<-cbind(Type_k,b)
c3_k_p<-c3_k
Big5_clus=Big5_1[Big5_1$cluster == as.character(3),]
for(r in 1:5){
  for(s in 1:2){
    c3_k_p[r,(s+1)]<-as.numeric(table(Big5_clus[,r]))[s]/km$size[3]
  }
}
c3_k_p

c3_k_p <- melt(c3_k_p, id.vars = 1)
ggplot(c3_k_p, aes(Type_k, value, fill = variable)) +
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Cluster 3") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  )
```


```{r}
#Cluster 4
c4_k<-cbind(Type_k,b)
c4_k_p<-c4_k
Big5_clus=Big5_1[Big5_1$cluster == as.character(4),]
for(r in 1:5){
  for(s in 1:2){
    c4_k_p[r,(s+1)]<-as.numeric(table(Big5_clus[,r]))[s]/km$size[4]
  }
}
c4_k_p

c4_k_p <- melt(c4_k_p, id.vars = 1)
ggplot(c4_k_p, aes(Type_k, value, fill = variable)) +
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Cluster 4") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  )
```

## Hierachical Clustering 
```{r}
d <- dist(total_Per1)  ## calculate the distance between each pair. 
hc <- hclust(d, method = "complete") ## agglomerative hierarchical clustering
plot(hc) 
```

```{r}
fviz_dend(hc, k = clu) 
```

```{r}
clusters <- cutree(hc, k = clu) 
cluster_complete <- total_Per1 %>% 
  add_column(cluster = factor(clusters)) 
```


```{r}
Big5_hi <- Big5 %>% add_column(cluster = factor(clusters)) 
Big5_hi<-select(Big5_hi,-matches("index"))
```


```{r}
Big5_hi1<-Big5_hi
Big5_hi1[,c(1:5)][Big5_hi1[,c(1:5)]=="y"]="1"
Big5_hi1[,c(1:5)][Big5_hi1[,c(1:5)]=="n"]="0"
```

#Conduct one-way analysis of variance regarding personality class
```{r}
aov_hi1 <- aov(cEXT~cluster, Big5_hi1)
aov_hi1
summary(aov_hi1)
```

```{r}
aov_hi2 <- aov(cNEU~cluster, Big5_hi1)
aov_hi2
summary(aov_hi2)
```

```{r}
aov_hi3 <- aov(cAGR~cluster, Big5_hi1)
aov_hi3
summary(aov_hi3)
```

```{r}
aov_hi4 <- aov(cCON~cluster, Big5_hi1)
aov_hi4
summary(aov_hi4)
```

```{r}
aov_hi5 <- aov(cOPN~cluster, Big5_hi1)
aov_hi5
summary(aov_hi5)
```

```{r}
cluster_hi<-Big5_hi %>% 
  count(cluster)
```

#Bar chart for the distribution of each personality trait
```{r}
Y<-c(0,0,0,0)
N<-c(0,0,0,0)
a<-data.frame(N,Y)
Cluster_h<-c(1:4)
cEXT_h<-cbind(Cluster_h,a)
cEXT_h_p<-cEXT_h
for(l in 1:clu){
  Big5hi_clus=Big5_hi[Big5_hi$cluster == as.character(l),]
  for(p in 1:2){
  cEXT_h[l,(p+1)]<-as.numeric(table(Big5hi_clus[,1]))[p]
  cEXT_h_p[l,(p+1)]<-as.numeric(table(Big5hi_clus[,1]))[p]/as.numeric(cluster_hi[l,2])
  }
}
cEXT_h
cEXT_h_p

cEXT_h_p <- melt(cEXT_h_p, id.vars = 1)
ggplot(cEXT_h_p, aes(Cluster_h, value, fill = variable)) + 
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Sociable vs Shy") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  ) 
```

```{r}
cNEU_h<-cbind(Cluster_h,a)
cNEU_h_p<-cNEU_h
for(l in 1:clu){
  Big5hi_clus=Big5_hi[Big5_hi$cluster == as.character(l),]
  for(p in 1:2){
  cNEU_h[l,(p+1)]<-as.numeric(table(Big5hi_clus[,2]))[p]
  cNEU_h_p[l,(p+1)]<-as.numeric(table(Big5hi_clus[,2]))[p]/as.numeric(cluster_hi[l,2])
  }
}
cNEU_h
cNEU_h_p

cNEU_h_p <- melt(cNEU_h_p, id.vars = 1)
ggplot(cNEU_h_p, aes(Cluster_h, value, fill = variable)) + 
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Neurotic vs Calm") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  ) 
```

```{r}
cAGR_h<-cbind(Cluster_h,a)
cAGR_h_p<-cAGR_h
for(l in 1:clu){
  Big5hi_clus=Big5_hi[Big5_hi$cluster == as.character(l),]
  for(p in 1:2){
  cAGR_h[l,(p+1)]<-as.numeric(table(Big5hi_clus[,3]))[p]
  cAGR_h_p[l,(p+1)]<-as.numeric(table(Big5hi_clus[,3]))[p]/as.numeric(cluster_hi[l,2])
  }
}
cAGR_h
cAGR_h_p

cAGR_h_p <- melt(cAGR_h_p, id.vars = 1)
ggplot(cAGR_h_p, aes(Cluster_h, value, fill = variable)) + 
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Friendly vs Uncooperative") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  ) 
```

```{r}
cCON_h<-cbind(Cluster_h,a)
cCON_h_p<-cCON_h
for(l in 1:clu){
  Big5hi_clus=Big5_hi[Big5_hi$cluster == as.character(l),]
  for(p in 1:2){
  cCON_h[l,(p+1)]<-as.numeric(table(Big5hi_clus[,4]))[p]
  cCON_h_p[l,(p+1)]<-as.numeric(table(Big5hi_clus[,4]))[p]/as.numeric(cluster_hi[l,2])
  }
}
cCON_h
cCON_h_p

cCON_h_p <- melt(cCON_h_p, id.vars = 1)
ggplot(cCON_h_p, aes(Cluster_h, value, fill = variable)) + 
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Organized vs Careless") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  ) 
```

```{r}
cOPN_h<-cbind(Cluster_h,a)
cOPN_h_p<-cOPN_h
for(l in 1:clu){
  Big5hi_clus=Big5_hi[Big5_hi$cluster == as.character(l),]
  for(p in 1:2){
  cOPN_h[l,(p+1)]<-as.numeric(table(Big5hi_clus[,5]))[p]
  cOPN_h_p[l,(p+1)]<-as.numeric(table(Big5hi_clus[,5]))[p]/as.numeric(cluster_hi[l,2])
  }
}
cOPN_h
cOPN_h_p

cOPN_h_p <- melt(cOPN_h_p, id.vars = 1)
ggplot(cOPN_h_p, aes(Cluster_h, value, fill = variable)) + 
  geom_col(width = 0.4, position = position_dodge(width = 0.5)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("#599bd7", "#ed7d32")) +
  theme_bw() +
  ggtitle("Insightful vs Unimaginative") +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray50"),
    plot.title = element_text(size = 24, hjust = 0.5)
  ) 
```

